---
title: "Math 459 study"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
```{r}
n=100
sam<-rgamma(n, 3, 2)
mean(sam)
ci<-c(mean(sam)-qnorm(0.975)*sd(sam)/sqrt(n), mean(sam)+qnorm(0.975)*sd(sam)/sqrt(n))
ci
plot(1.5, xlim = c(0.9, 1.1), ylim = c(1.4, 1.6))
draw<-function(i) {
  set.seed(100)
  n=100*i
sam<-rgamma(n, 3, 2)
points(mean(sam))
}
for (i in 1:1000) {
  draw(i)
}
## Exercise 5.2
n=1000
x<-rgamma(n, 3, 2)
mean(x)
ci<-c(mean(x)-qnorm(0.975)*sd(x)/sqrt(n), mean(x)+qnorm(0.975)*sd(x)/sqrt(n))
ci
xq<-quantile(x, c(0.1, 0.9))
y<-x^2*exp(-x)/(1+x+1/x)
mean(y)
yq<-quantile(y, c(0.1, 0.9))
ciy<-c(mean(y)-qnorm(0.975)*sd(y)/sqrt(n), mean(y)+qnorm(0.975)*sd(y)/sqrt(n))
ciy
par(mfrow = c(2, 1))
#hist for x
hist(x, probability = TRUE, breaks = seq(0, 7, 0.25), xlim = c(0, 10), ylim = c(0, 0.6), xlab = "x")
lines(density(x), lty = 2, lwd = 2, col = "green")
l<-seq(0, 7, 0.01)
lines(l, dgamma(l, 3, 2), lty = 1, lwd = 1, col = "red")
abline(v = c(mean(x), ci, xq), lty = 2, lwd = 2, col = "blue")
abline(v=c(1.5, qgamma(c(0.1, 0.9), 3, 2)), lty = 1, lwd = 1, col ="orange")
legend(4,0.6,c("MC estimates","True values"),lty=c(2,1),lwd=c(2,2))


#hist for y
hist(y, probability = TRUE, breaks = seq(0, 0.2, 0.005), ylim = c(0, 32))
lines(density(y), lty = 2, lwd = 2, col = "green")
abline(v=c(mean(y), yq, ciy), lty = 1, lwd = 1, col = "blue")

## Exercise 5.3
a<-rexp(100000)
mu<-(sum(a/(a+1))/100000)/(sum(1/(a+1))/100000)
mu
k<-function(x){exp(-x)/(x+1)}
c=integrate(k, 0, Inf)$value
f=function(x){ (1/ 0.5963473624)*exp(-x)/(x+1) } integrate(f=f,lower=0,upper=Inf)$value; 
xf= function(x){ x*(1/0.5963474)*exp(-x)/(x+1) }
mu= integrate(f=xf,lower=0,upper=Inf)$value

## Exercise 5.4
n<-1000
x<-rgamma(n, 3, 2)
y<-rnorm(x, sqrt(x))
r<-y/(x+sqrt(abs(y)))
mean(r)
ci<-c(mean(r)-qnorm(0.975)*sd(r)/sqrt(n), mean(r)+qnorm(0.975)*sd(r)/sqrt(n))
ci
qr<-quantile(r, c(0.1, 0.9))
qr
hist(r, probability = TRUE, breaks = seq(-1.2, 1.8, 0.15), xlim = c(-1.2, 1.8), ylim = c(0, 1.4))
lines(density(r), lty = 2, lwd = 2, col = "green")
abline(v = c(mean(r), qr, ci), lty = 1, lwd = 1, col = "blue")

## Exercise 5.5
n<-20000
x<-rgamma(n, 3, 2)
y<-exp(-x)*sqrt(x/(x+1))
num<-0
for (i in 1:n) {
  if(y[i]>0.3){
    num<-num+1
  }
}
p<-num/n
p
ci<-c(p-qnorm(0.975)*sqrt(p*(1-p)/n), p+qnorm(0.975)*sqrt(p*(1-p)/n))
ci
hist(y, probability = TRUE, breaks = seq(0, 0.4, 0.008))
lines(density(y), lty = 2, lwd = 2, col = "green")
abline(v = c(p, ci, 0.3), lty = 2, lwd = 1, col = "blue")

## Exercise 5.6
plot(seq(0,pi/2,0.01),sin(seq(0,pi/2,0.01)), type="l",lwd=3,xlab="y", ylab="x") abline(v=c(0,pi/2),lty=3); abline(h=c(0,1),lty=3)
text(0.2,0.4,"x = sin(y)"); text(1,0.4,"C"); text(0.35,0.8,"Complement of C") text(1.52,0.06,"pi/2")

plot(seq(0,pi/2,0.01),sin(seq(0,pi/2,0.01)), type="l",lwd=3,xlab="y", ylab="x") abline(v=c(0,pi/2),lty=3); abline(h=c(0,1),lty=3)
text(0.2,0.4,"x = sin(y)"); text(1,0.4,"C"); text(0.35,0.8,"Complement of C") text(1.52,0.06,"pi/2")

##Exercise 5.7
n<-100
x<-rgamma(n, 3, 2)
mean(x)
ci<-c(mean(x)-qnorm(0.975)*sd(x)/sqrt(n), mean(x)+qnorm(0.975)*sd(x)/sqrt(n))
ci #no

ans<-c(rep(0.0, 5))
num<-0
t<-1
k<-c(200, 500, 1000, 10000, 100000)
for (i in 1:5) {
  n<-k[i]
  x<-rgamma(n, 3, 2)
mean(x)
ci<-c(mean(x)-qnorm(0.975)*sd(x)/sqrt(n), mean(x)+qnorm(0.975)*sd(x)/sqrt(n))
ans[t]<-ci[2]-ci[1]
t<-t+1
if(ci[2]>1.5){
  if(ci[1]<1.5){
    num<-num+1
  }
}
}
num
ans

da<-0
for (i in 1:100) {
  n<-100
x<-rgamma(n, 3, 2)
ci<-c(mean(x)-qnorm(0.975)*sd(x)/sqrt(n), mean(x)+qnorm(0.975)*sd(x)/sqrt(n))
if(ci[1]<1.5){
  if(ci[2]>1.5){
    da<-da+1
  }
}
}
p<-da/100
p

dada<-c(rep(0, 4))
l<-c(200, 500, 1000, 10000)
da<-0
for(j in 1:4){
  for (i in 1:l[j]) {
  n<-l[j]
x<-rgamma(n, 3, 2)
ci<-c(mean(x)-qnorm(0.975)*sd(x)/sqrt(n), mean(x)+qnorm(0.975)*sd(x)/sqrt(n))
if(ci[1]<1.5){
  if(ci[2]>1.5){
    da<-da+1
  }
}
}
p<-da/n
dada[j]<-p
}
dada

## Exercise 5.8

## Exercise 5.9

# Reject sampling 
## Exercise 5.10
u<-runif(1000, 0, 1)
x<--log(1-u)
y<-1-(u+1)*exp(-u)

```